### 2020-12-17 Thesis-Chapter6-ThreatModel.tex
Work on risk analysis

\ii{S6}, \ii{T1}, \ii{T3}, \ii{I1}, \ii{I3}, \ii{I6}, \ii{D1}, \ii{D2}, and \ii{E1} \ii{E2} are each low-risk. They
either they fail to produce useful results, can be reasonably mitigated, or are a threat that is already present in the
baseline depicted in \mysec{sec-basic-dar}. Although these threats are not fatal flaws to a design, it is important for
a design to consider and mitigate the risk they pose. Unless they appear in combination with other threats, they are do
not deserve more discussion.

\ii{S1}, \ii{S2}, \ii{S3}, \ii{S4}, \ii{S5}, \ii{T2}, \ii{T4}, \ii{R1}, and \ii{I2} are all higher-risk threats to the
security, trustworthiness, and effectiveness of the proposal. However, they can be addressed through a set of related
requirements: require destructive disassembly of the device to access the \ac{EA} hardware interface, require the device
to be physically present on LEA premises the entire duration it is unlocked, and grant only a handful of LE facilities
the lawful right to use the \ac{EA} mechanism. Requiring destructive disassembly entirely precludes certain attacks.
Requiring the device to be on LEA premises prevents attackers from manipulating LE into achieving the attackers' ends.
Limiting the number of law enforcement facilities that can participate in the \ac{EA} system prevents LE impersonation
attacks. Together, these mitigations make the proposal more resistant to attack.

\ii{R2}, \ii{R3}, and \ii{R4} are repudiation attacks that belie the system's potential for abuse. The system relies on
legal process and cooperation of several parties. Even in the U.S., the legal process can involve secret courts, secret
investigation, and secrecy orders on the vendor \cite{shamsi_2011}. Under these conditions, transparency is difficult to
achieve. A destructive disassembly requirement provides non-repudiation that the device was unlocked, if and only if one
has physical access to the device. Technically enforced transparency into device access requests and responses would
grant non-repudiation at a broader level. \ldawmsr does not include a mechanism for the feature, though other \ac{DAR}
\ac{EA} proposals do \cite{phan_key_2017} \cite{servan_schreiber_jje_2020} \cite{goldwasser_public_2017}. Unfortunately,
building this feature into a proposal makes it potentially vulnerable the hawkish lawmaker, who may consider too much
transparency to be an anti-feature.

Finally, there are the threats of \ii{I4}, \ii{I5}, and \ii{E3}, which each represent the disclosure of unlock artifact
data, the DID-DSK database. These threats create a large amount of risk that cannot be safely mitigated. To store so
much sensitive data in a central database creates a high-value target for foreign intelligence and cyber criminals. The
vendor needs to protect this database from the most advanced attackers in the world while regularly updating and
accessing it. \Acp{HSM} and robust security policies would make that a difficult task. The data will almost certainly
leak eventually. The effects of such an event would depend on who stole the unlock artifacts. Criminals would use the
data for personal and financial gain; foreign intelligence and authoritarian regimes would use it to spy on their
enemies. In the worst-case scenario, anyone with specialized tools and disregard for the law could get into any
compliant device after dissembling it and waiting through the time vault.

@@

\paragraph*{Transparency} \ldawmsr provides transparency to the device user, but does not provide transparency to the
public. Due to destructive disassembly (or the hardware transparency mechanism), whether a device has been accessed
using this method is irrefutable. However, this can only be confirmed if the device is available. Neither the user nor
the public can detect if a device is lawfully accessed under secretive conditions or is stolen and unlocked by
criminals. This leaves allows the potential for government abuse---though again with the caveat that physical possession
requirements mean it cannot be abused without a trace.

\paragraph*{Law enforcement utility} \ldawmsr performs a few tradeoffs between security and law enforcement utility. The
requirements to have physical possession of the device, to wait through the time vault, and to limit the number of
authorized law enforcement laboratories each create barriers to usability. The physical possession requirement is far
too important for security and civil liberties to sacrifice for utility. Furthermore, law enforcement, and search and
seizure law generally, is geared towards physical evidence already. The time vault prevents against time-sensitive
threats, though destructive disassembly (not part of the original proposal) may be enough to cover these cases as well,
so the time vault could be decreased without significant impact. Limiting the number of laboratories able to use the
system reduces the risk of spoofing attacks; local law enforcement would have to cooperate with one of these special
laboratories, such as a regional \ac{FBI} office. (This really just shifts the spoofing threat up a level, though the
shift is appropriate.) In the end, law enforcement still has a reliable way to get into lawfully seized devices.
\ldawmsr upholds its end, but the government must fund the \ac{FBI} operation and cultivate cooperation between local
and federal agencies.

\paragraph*{Economic impact} Expenses to the vendor fall into three categories---the costs of implementing the design,
running the system, and absorbing lost business. Even if a proposal like \ldawmsr was refined enough to be implemented,
the vendor would need to update hardware designs and create the software systems to get it started. Once in use, the
vendor would face considerable costs in running it securely, due to the difficulty or safely accessing and updating the
unlock artifacts. Finally, the vendor would certainly lose privacy-conscious customers to small businesses, foreign
competitors, or resellers offering pre-\ac{EA} devices. The scale of these costs relative to device manufacturer's large
size is unclear. Costs to the government include the \ac{FBI} laboratory cost and the cost of law enforcement resources
and training. Government reimbursement for vendor compliance costs has precedent in laws like \acs{CALEA}, and could be
applied to a \ac{DAR} \ac{EA} regulation as well \cite{edwards_hr4922_1994}.

>>>>

\ii{S6}, \ii{T1}, \ii{T3}, \ii{I1}, \ii{I3}, \ii{I6}, \ii{D1}, \ii{D2}, and \ii{E1} \ii{E2} are each low-risk. They
either fail to produce useful results, can be reasonably mitigated, or are a threat that is already present in the
baseline depicted in \mysec{sec-basic-dar}. Although these threats are not fatal flaws to a design, it is important for
a designer to consider and mitigate the risk they pose. Unless they appear in combination with other threats, they do
not deserve more discussion.

\ii{S1}, \ii{S2}, \ii{S3}, \ii{S4}, \ii{S5}, \ii{T2}, \ii{T4}, \ii{R1}, and \ii{I2} are all higher-risk threats to the
security, trustworthiness, and effectiveness of the proposal. However, they can be mitigated through a set of related
requirements: require destructive disassembly of the device to access the \ac{EA} hardware interface, require the device
to be physically present on LEA premises the entire duration it is unlocked, and grant only a handful of LE facilities
the lawful right to use the \ac{EA} mechanism. Requiring destructive disassembly entirely precludes certain attacks.
Requiring the device to be on LEA premises prevents attackers from manipulating LE into achieving the attackers' ends.
Limiting the number of LE facilities that can participate in the \ac{EA} process prevents LE impersonation attacks.
Together, these mitigations make the proposal more resistant to attacks.

\ii{R2}, \ii{R3}, and \ii{R4} are repudiation attacks that belie the system's potential for abuse. The system relies on
legal processes and cooperation of several parties. Even in the U.S., the legal process may involve secret courts,
secret investigations, and secrecy orders on the vendor \cite{shamsi_2011}. Under these conditions, transparency is
difficult to achieve. A destructive disassembly requirement provides non-repudiation that the device was unlocked, if
and only if one has physical access to the device. Technically enforced transparency into device access requests and
responses would grant non-repudiation at a broader level. \ldawmsr does not include a mechanism for the feature, though
other \ac{DAR} \ac{EA} proposals do \cite{phan_key_2017} \cite{servan_schreiber_jje_2020} \cite{goldwasser_public_2017}.
Unfortunately, building this feature into a proposal makes it potentially vulnerable the hawkish lawmaker, who may
consider too much transparency to be an anti-feature.

Finally, there are the threats of \ii{I4}, \ii{I5}, and \ii{E3}, which each represent the disclosure of unlock artifact
data (the DID-DSK database). These threats create a large amount of risk that cannot be safely mitigated. Storing so
much sensitive data in a central database creates a high-value target for foreign intelligence and cyber criminals. The
vendor needs to protect this database from the most advanced attackers in the world while regularly updating and
accessing it. \Acp{HSM} and robust security policies would make that a difficult task. The data will almost certainly
leak eventually. The effects of such an event would depend on who stole the unlock artifacts. Criminals would use the
data for personal and financial gain; foreign intelligence and authoritarian regimes would use it to spy on their
enemies. In the worst-case scenario, anyone with specialized tools and disregard for the law could get into any
compliant device after disassembling it and waiting through the time vault.

@@

\paragraph*{Transparency} \ldawmsr provides transparency to the device user, but does not provide transparency to the
public. Due to destructive disassembly (or the hardware transparency mechanism), whether a device has been accessed
using this method is irrefutable. However, this can only be confirmed if the device is available. Neither the user nor
the public can detect if a device has been unlocked under secretive conditions, whether lawfully or criminally. This
leaves allows the potential for government abuse---though again with the caveat that physical possession requirements
mean it cannot be abused without a trace.

\paragraph*{Law enforcement utility} \ldawmsr includes a few tradeoffs between security and law enforcement utility. The
requirements to have physical possession of the device, to wait through the time vault, and to limit the number of
authorized law enforcement laboratories all create barriers to usability. The physical possession requirement is far too
important for security and civil liberties to sacrifice for utility. Furthermore, law enforcement, and search and
seizure law generally, is geared towards physical evidence already. The time vault prevents against time-sensitive
threats, though destructive disassembly (not part of the original proposal) may be enough to cover these cases as well,
so the time vault could be decreased without significant impact. Limiting the number of laboratories able to use the
system reduces the risk of spoofing attacks; local law enforcement would have to cooperate with one of these special
laboratories, such as a regional \ac{FBI} office. (This really just shifts the spoofing threat up a level, though the
shift is appropriate.) In the end, law enforcement still has a reliable way to get into lawfully seized devices.
\ldawmsr upholds its end, but the government must fund the \ac{FBI} operation and cultivate cooperation between local
and federal agencies.

\paragraph*{Economic impact} Expenses to the vendor fall into three categories---the costs of implementing the design,
running the system, and absorbing lost business. Even if a proposal like \ldawmsr was refined enough to be implemented,
the vendor would need to update hardware designs and create the software systems to get it started. Once in use, the
vendor would face considerable costs in running it securely due to the difficulty of safely accessing and updating the
unlock artifacts. Finally, the vendor would certainly lose privacy-conscious customers to small businesses, foreign
competitors, or resellers offering pre-\ac{EA} devices. The scale of these costs relative to device manufacturer's large
size is unclear. Costs to the government include the \ac{FBI} laboratory cost and the cost of law enforcement resources
and training. \acs{CALEA} includes provisions for government reimbursement of vendor compliance costs, and a similar
provision could be applied to a \ac{DAR} \ac{EA} regulation \cite{edwards_hr4922_1994}.
